Complete Real-Time Liver Model including Glisson Capsule, Vascular Network and Parenchyma

### 2013-03-01 Doc/Miccai2013/miccai2013.tex
ADD: graph showing the force evoluation when adding the membrane
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@538 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\subsection{Global Deformations}
\CD{ Experiments demonstrate that capsule plays a role at local level, but still, maybe not so important to model the capsule for more global deformation...
+ What are the applications for modeling the global deformations of the liver (training and planning simulation, physics-based registration, augmented reality,)}

\TG{!!!}

%Test 1) Global deformation of liver under gravity
%  * show that there is a difference between simple homogeneous material
%    and material with capsule
%  * include blood vessels

>>>>

\subsection{Global Deformations}

\begin{figure}[htb]
  \centering
    \includegraphics[width=.95\textwidth]{forceEvolution.pdf}
  \caption{\label{fig-aspiration}Evolution of forces during elastic warping.}
\end{figure}
